### 2012-06-25 manuscript/textmine.Rmd
added some table text

@@

@@

>>>>

#### Table 1. Sources of scientific literature, their content type provided via web services, whether rOpenSci has an R packages for the service, and where to find the API documentation.

@@

#### Table 2. Tools for text mining science literature.

Tool           |  Platform            | Services              | URL
-------------- | -------------------- | --------------------- | ---------------------
PMC Miner      | Python               | PubMed                | http://bit.ly/L29ekY
rOpenSci       | R                    | See Table 1           | http://ropensci.org/
PMC Miner      | Python               | PubMed                | http://bit.ly/L29ekY
PMC Miner      | Python               | PubMed                | http://bit.ly/L29ekY
PMC Miner      | Python               | PubMed                | http://bit.ly/L29ekY
PMC Miner      | Python               | PubMed                | http://bit.ly/L29ekY
PMC Miner      | Python               | PubMed                | http://bit.ly/L29ekY
PMC Miner      | Python               | PubMed                | http://bit.ly/L29ekY
PMC Miner      | Python               | PubMed                | http://bit.ly/L29ekY
PMC Miner      | Python               | PubMed                | http://bit.ly/L29ekY
PMC Miner      | Python               | PubMed                | http://bit.ly/L29ekY
PMC Miner      | Python               | PubMed                | http://bit.ly/L29ekY

@@

### To read:
+ http://lintool.github.com/MapReduceAlgorithms/index.html
+
